%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Anveen Private Ltd.} % Organization
    {Windsor, Canada, Remote} % Location
    {May. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working as a full stack software developer writing efficient and scalable RESTful API's in PHP and responsive Vue components for the web app.}
        \item {Currently building a subscription tracking web app from the ground up. }
        % \item {Also have built a project management web app to track or manage ongoing projects on the industry from the ground up. }
        \item {Designed an overall microservice architecture inside WordPress codebase that is responsible for handling any API request efficiently from the client-side. The company wanted this so badly to achieve \textbf{single page application} taste inside WordPress. So, I've made it possible to recognize Vue components inside WordPress and talk to them using RESTful APIs.}
        \item {Implemented several API microservices in PHP flowing MVC design pattern.}
        \item {Deployed the app on the AWS several times to test the app on production mode.}
         \item {Write documentation for the projects using \textbf{docusaurus}  and write meaningful comments for each and every function, class, route, etc. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student \& Software Developer} % Job title
    {Premier University} % Organization
    {Chittagong, Bangladesh} % Location
    {Jun. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Have worked as a full stack developer for a contract based web application. }
        \item {Implemented RESTful API in Laravel and responsive web components in VueJS and Vuex. }
        \item {Built an overall service infrastructure utilizing Laravel REST APIs, VueJS, Vuex, Vue Router, Apache, MySQL etc.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
